### 2016-03-06 ch05-initvals/initial-values.tex
Address some comments from Tom (CH05)

Parametric identification of \gls{LTI} systems from either input/output data or non-parametric frequency response data, has been well developed as evidenced by published literature~\citep{Pintelon2012,Ljung1999,Schoukens1999,Pintelon1998}.
Many of such parametric identification algorithms, however, require solving non-linear or non-convex optimization problems.
This often involves an iterative algorithm to produce the optimal model.
 The resulting model, however, depends on which initial estimates are used to start up the optimization process: typically one can end up in local minima.
 Hence, good initial estimates are essential to obtain a high quality model estimate.
 In this chapter, the \gls{MLE} is used as a proxy for any parametric transfer function estimator, since the \gls{MLE} is both consistent and efficient and is a commonly used estimator.
 Since the initial value generation method are not specifically tailored towards the \gls{MLE}, other parametric identification frameworks are likely to benefit from these improved starting values.

@@

The main aim and contribution of this chapter is to demonstrate that smoothing a measured \gls{FRF} helps to avoid local optima during the parametric estimation of the \gls{MLE} of a transfer function, using classical (deterministic) optimization algorithms.
Hence, such techniques make it possible to increase the ``success rate'' (i.e. the probability that a good model, or even the global optimum, is obtained) of such a system identification step considerably.

@@

The rest of the chapter is structured as follows. 
\secref{se:ProbForm} covers the problem formulation. 
\secref{se:MethodEg} presents the methodology for obtaining the initial estimates, and their influence on the success rate of the \gls{MLE}. 
This is followed by \secref{se:Demo} and \secref{se:ExpMeas}, which are demonstrations of the improved initial estimates on simulation and experimental data, respectively.
In \secref{se:Generality} the generality of the results is investigated briefly.
The computational effort and recommendations for practical implementations are given in \secref{sec:initvals:computation}.
Ultimately, concluding remarks are presented in \secref{se:Conclusion}.

\section{Problem formulation}\label{se:ProbForm}
%\begin{itemize}
%\item
%Block schematic of the output error framework

%\JL{In this section, the assumptions on the system and the noise are given, and the associated Maximum Likelihood estimator, formulated in the frequency domain. The latter turns out to be a non-convex function in the parameters, requiring initial estimates. The obtention of those is discussed in the subsequent section.}

@@

The maximum likelihood estimate of the parameter vector $\theta$  containing the coefficients of the $A$, $B$ and $I$  polynomials is obtained by solving the optimization problem
\begin{equation}
  \hat{\theta} = \arg\min_\theta V(\theta) \text{.}
\end{equation}
Since the noise $v(t)$ is assumed to be Gaussian, $V(\theta)$ accords to the weighted least squares cost function~\citep[Section 9.11]{Pintelon2012}:
\begin{equation}\label{eq:MLEcf}
V(\theta) = \sum_{k=1}^{N/2-1}\frac{|\varepsilon(k,\theta)|^2}{\sigma_\varepsilon^2(k,\theta)}
\end{equation}
for $N$ measurements and when $\varepsilon$ denotes the error in equation \eqref{DFTspectra},  \emph{viz}.:
\begin{align}
\varepsilon(k,\theta) = A(k,\theta)Y(k) - B(k,\theta)U(k) - I(k,\theta)\text{.}
\end{align}
The variance of the error is of the form:
\begin{equation}\label{eq:sigmaEps}
\begin{split}
\sigma_\varepsilon^2(k,\theta) 
  &=  |A(k,\theta)|^2\sigma_Y^2(k) 
   +  |B(k,\theta)|^2\sigma_U^2(k) \\
  &- 2\RealPart \left( A(k,\theta) \overline{B(k,\theta)} \sigma_{YU}(k) \right)
\end{split}
\end{equation}
where $\sigma_Y^2$ is independent of $k$ for white noise, %assumed to be a known error variance \comment{JL: why should the error variance be known? where do you use that? how do you compute it?} of the measured output spectrum $Y$ \comment{JL: relate the output error variance with the variance of $v(t)$. Isn't it the same thing?},
%\comment{this is true for white noise, and for the scaling of the DFT by $\sqrt{N}$. I think it is more clear to use the frequency domain variance instead: $\sigma_Y^2$}
and the input error variance is assumed to be zero, i.e. $\sigma^2_U=0$, and similarly, the covariance $\sigma_{YU} = 0$.
Here, $\overline{B}$ denotes the complex conjugate of $B$.
%\comment{use $\sigma^2_U$ instead}

@@

%\JL{The Generalized Total Least Squares (GTLS) and the Bootstrapped Total Least Squares (BTLS) have been discussed in \citep{pintGuil1998}. These are modifications of \eqref{eq:MLEcf}, which still take into account the noise information, while keeping the quadratic nature w.r.t.\ $\theta$. These estimators preserve consistency (which is an asymptotic behaviour, i.e.\ for $N\to\infty$). Their finite sample behaviour is prone to be improved by the FRF smoothing tools, described below.}

@@

%\JL{
The \gls{RFIR} estimator is formulated in the time domain. 
It estimates the impulse response of a discrete time system as the minimizer of the following regularized least squares objective function:
\begin{align}\label{eq:hRFIRdef}
\hat g_{\mathrm{RFIR}} &= \argmin_{g} \norm{y - g \ast u }^2 + \sigma^2 g^{\TT}P^{-1}g
\end{align}
where $g$ is the vectorized impulse response $g(t)$, with $t = 0,1,\cdots,n_h - 1$, assuming that the impulse response is $n_g$ samples long. 
Furthermore, $g\ast u$ is the convolution of $g$ with the input signal $u$, and $P\in \mathbb{R}^{n_g\times n_g}$ is the kernel matrix. 
Note that \eqref{eq:hRFIRdef} is quadratic in $g$, such that $\hat g_{\mathrm{RFIR}}$ can be computed analytically in a single step.
The kernel matrix $P$ embodies prior knowledge on the system to be estimated. 
Here, the \gls{DCkernel}~\citep{Chen2012,Pillonetto2010} is used. 
Specifically, the element at $t_1,t_2$ of $P$ is given by
\begin{equation}
P(\alpha,\beta)_{t_1,t_2} = e^{-\alpha|t_1 - t_2|}e^{-\beta(t_1 + t_2)/2}
\end{equation}
 for $t_1,t_2 \in \left\{0,1,\cdots,n_h - 1\right\}$ which makes the estimated impulse response to be an exponentially decaying function of $t$ with decay rate $\beta^{-1}$, and correlation length $\alpha^{-1}$. 
 The latter \emph{hyperparameters} $\alpha$, $\beta$ and $\sigma$ are determined using Empirical Bayes, i.e. as the maximizers of the \gls{LML} of the measured output signal~\citep{Chen2013}:
\begin{align}
\mathrm{LML}(y) = -y^{\TT}\Sigma(\alpha,\beta,\sigma)^{-1}y - \log |\Sigma(\alpha,\beta,\sigma)| \text{,}
\end{align}
where $\Sigma(\alpha,\beta, \sigma) = \sigma^2 \I + \phi^{\TT}P(\alpha,\beta)\phi$ and $\phi$ is a Toeplitz matrix constructed with $u$. 
This problem is solved using \mcode{fmincon} in \MATLAB.

An implementation of the \gls{RFIR} estimator is available as the \mcode{arx} function in the System Identification Toolbox since \MATLAB~2013b with $\mathtt{na} = 0$, $\mathtt{nb} = n_g$, $\mathtt{nk}=0$ and regularization enabled in \mcode{arxoptions}. 
The hyperparameters can be determined via \mcode{arxregul}.
More information about the \gls{RFIR} estimator can be found in
~\citep{Pillonetto2010,Chen2012}. 
The \gls{DFT} of the obtained regularized estimate of the impulse response $\hat g_{\mathrm{RFIR}}$ of the system yields a smoothed estimate of the \gls{FRF}.
\end{enumerate}

@@

A particular initial estimate is deemed \emph{successful} if the optimization of the MLE cost with the raw input-output data inserted in equation~\eqref{eq:MLEcf}, reaches the \emph{best local optimum} when iteration is initiated with the selected initial value/estimate.

@@

The capability is quantified by defining the success rate of the initial estimate as the probability that the identification algorithm reaches the \emph{best local optimum} when the selected initial estimate is used. %using the selected initial estimate.

The success rate $\eta$ is expressed mathematically as a probability function, consistent with Conjecture \ref{conj1}, \emph{viz}:
\begin{equation}
\eta_{\bullet}=\Prob{\model{\bullet}=\model{\trueSymbol}}
\end{equation}
In practice, and since the iterative algorithm usually does not reach the local optimum precisely, the above definition is relaxed to the form
\begin{equation}\label{eq:successrateTol}
\eta_{\bullet} \isdef \Prob{ \norm[2]{\model{\bullet} - \model{\trueSymbol}} < tol}
\end{equation}
with $tol$ a numerical tolerance that will be specified later on.
\begin{remark}
For an automated approach, it is better to define the success rate in terms of relative errors on the transfer function, i.e.
\begin{equation}
\eta_{\bullet} = \Prob{ \norm[2]{\model{\bullet}-\model{\trueSymbol}} < rel.tol  \norm[2]{\true{G}}}
\text{.}
\end{equation}
\end{remark}
\begin{remark}
In this chapter, the absolute criterion is used.
However, the results are equivalent for a relative criterion when the separation between successful and failed estimates is large since then observed success rate $\eta$ is only mildly sensitive towards the tolerance $tol$ (or $rel.tol$) when the tolerance is chosen with care.
Consequently, one can easily determine the equivalent relative tolerance from the absolute one using $tol = rel.tol \norm[2]{\true{G}}$.
\end{remark}

% \comment{JL to EG: It is better to implement the success rate as given in \eqref{eq:successrateTol}, because that can more easily be adhered. Note that it is not obvious to determine a tolerance on the difference between the estimated and the true model, because that depends on the noise variance of the estimate. On the other hand, the tolerance in \eqref{eq:successrateTol} and \eqref{eq:toldef} is independent of the noise variance.
%\comment{\EG{it is implemented that way now}}
% }

The norm used in equation \eqref{eq:successrateTol} is defined as
\begin{align}
\norm[2]{G(z)} &\isdef \sqrt{\frac{1}{2\pi}\int_0^{2\pi} |G(e^{-j\omega})|^2\ \mathrm{d}\omega}& \text{ for discrete time,}\\
\norm[2]{G(s)} &\isdef \sqrt{\frac{1}{2\pi}\int_{-\infty}^{+\infty} |G(j\omega)|^2\ \mathrm{d}\omega}& \text{ for continuous time}
\end{align}
 which, in practice, is computed by using the adaptive global quadrature algorithm provided by the MATLAB function \code{integral}.
%\comment{EG: The exact implementation is in the L2Norm function. Basically, either numerical or symbolic integration can be used (as our models are parametric), but both yield equally workable results (cfr. testDistance). I picked a full numerical approach as the symbolic one doesn't always work on my computer.}
%\JL{The success rate in \eqref{eq:successrateTol} will be estimated via Monte Carlo simulations, further\ML{/later} on.}
The success rate in equation \eqref{eq:successrateTol} is estimated via Monte Carlo simulations in  Section \ref{se:CompuSR}.

% !TEX root =  InitialValuesPaper.tex

\section{Demonstration}\label{se:Demo}

@@

\subsubsection{Simulation}
A Monte Carlo simulation was set up to determine the success rate of the estimator with different initial estimates for the following ranges %\comment{ML: To modify text!}
\begin{itemize}
\item of SNR: 
              $-20   \unit{dB}$, 
              $-16.7 \unit{dB}$, 
              $-13.3 \unit{dB}$, 
              $-10   \unit{dB}$, 
              $- 7.8 \unit{dB}$, 
              $- 5.6 \unit{dB}$, 
              $- 3.3 \unit{dB}$, 
              $- 1.1 \unit{dB}$, 
              $  1.1 \unit{dB}$, 
              $  3.3 \unit{dB}$, 
              $  5.6 \unit{dB}$, 
              $  7.8 \unit{dB}$, 
              $ 10   \unit{dB}$, 
              $ 13.3 \unit{dB}$, 
              $ 16.7 \unit{dB}$ and
              $ 20   \unit{dB}$
\item of number of samples $N$ is $3\,368$ or $4\,462$ for the first system whose quality factor $Q= 6 \unit{dB}$,
\item and of number of samples $N$ is $20\,250$ or $26\,792$ for the second system whose quality factor $Q = 20\unit{dB}$.
\end{itemize}
\TODO{johan: tijdsconstantes geven}
One can, equivalently, express the experiment length as the number $N_{3\unit{dB}}$ of frequency bins that lie within the $3\unit{dB}$ bandwidth of the system.
The $3\unit{dB}$ bandwidth is defined as the frequency band where the magnitude of the transfer function is, at most, $3\unit{dB}$ below its maximum as indicated in \figref{fig:exampleFRF}.
For both systems, $N$ was chosen such that $N_{3\unit{dB}}$ is respectively $36$ or $48$.
For each value-pair $(\SNR, N_{3\mathrm{dB}})$ and both systems, $n_{\mathrm{MC}} = 200$  simulations and estimations were performed.
Each individual simulation yields an estimate of the model based on which one can determine whether the estimation was successful or not.
This allows to empirically estimate the success rate $\eta$ in equation \eqref{eq:successrateTol} as the proportion of the successes from the $N_{\MC} = 200$ runs.

%\ML{
\subsubsection{Illustrative Example}
In particular, the simulation for each pair $(\mathrm{SNR}, N_{3\mathrm{dB}})$ yields 200 estimates per initial value strategy.
This is illustrated graphically in \figref{fig:single-sim} for the value-pair $(-1.1\unit{dB},48)$ of the system with $Q = 6 \unit{dB}$, where the obtained distances $\norm{\model{\bullet} - \model{\trueSymbol}}$ are shown for the different strategies, and sorted by an ascending norm.
This effectively shows an empirical cumulative distribution function of the distance measure $\norm{\model{\bullet} - \model{\trueSymbol}}$ as sampled by the Monte Carlo algorithm.%}

%\JL{One observes:}
\subsubsection{Pertinent Observations}
With reference to \figref{fig:single-sim}, the following observations are worth noting: 
%\EG{
\begin{itemize}
\item The actual parametric estimates, based on the different initial estimates, have distinct behaviors with respect to their distance from $\model{\trueSymbol}$.
Two major classifications can be made:
\begin{enumerate}
  \item `good' estimates which have $\|\model{\bullet} - \model{\trueSymbol} \|_2 < tol \approx 6 \cdot 10^{-5}$,
  \item `poor' estimates which are much further from $\model{\trueSymbol}$.  This is caused by the local optima.
\end{enumerate}
\item
The obvious jump of the observed distances of the final parametric estimates shows that both classes can be separated reliably.
The index at which this jump occurs is a direct (visual) indication of the success rate $\eta$ of the corresponding strategy to obtain initial values.
This indicates $\frac{147}{200} \approx 74\%$ success for the existing methods, $\frac{189}{200} \approx 95\%$ for the truncation method and $100\%$ for RFIR in \figref{fig:single-sim}.
\end{itemize}
%}

@@

In \figref{fig:successRateVS_SNR36N3dB}, the success rate (and its $95\%$ confidence interval $\mathrm{CI}$) obtained from the Monte Carlo simulations is shown to compare the proposed method with previously existing approaches.
Note that the empirical count of successes $n_{\mathrm{success}}$ out of the $N_{\MC}$ total observations is binomially distributed with success rate $\eta$.
The computation of confidence bounds of such a variable is not obvious due to the discrete nature of the variable: $n_{\mathrm{success}}$ can only attain a discrete set of values: $\Set{0,1,\ldots, N_{\MC}}$ whereas the true success rate $\eta$ is real-valued (but limited to the interval $[0,1]$).
The inherent discreteness of $\hat{\eta} \isdef n_{\mathrm{success}}/N_{\MC}$ and the difficulties this presents has sparked a fair amount of research to compute confidence bounds~\citep{Barnard1947Significance,Mato1997,Ross2003,Clopper1934}.
A simple way to deal with this problem, is to make use of the central limit theorem which states that $n_{\mathrm{success}}/N_{\MC}$ is approximately normally distributed when $N_{\MC} \to \infty$.
In doing so, one e.g. obtains the Wald confidence bounds~\citep{Ross2003}:
\begin{equation}
\mathrm{CI}_{\mathrm{Wald}} \isdef \hat{\eta} \pm z_{1-\alpha/2} \sqrt{\hat{\eta} (1-\hat{\eta}/N_{\MC})}
\end{equation}
with $\alpha = 1 - 0.95$ for $95\%$ confidence bounds and $z_{1-\alpha/2}$ is the $1-\alpha/2$ quantile of a standard normal distribution, i.e. $z_{\beta} \isdef \mathrm{CDF}_{\NormalDistribution}^{-1}(\beta)$
which requires inversion of the \gls{CDF} of a normal distribution.
However, such an approximation is overly optimistic when $n_{\mathrm{success}}$ approaches the boundaries of its domain (i.e. when $\eta \approx 0$ or $\eta \approx 1$) since normal confidence regions are always symmetrical whereas the actual success rate is inherently bounded as $0 \leq \eta \leq 1$~\citep{Ross2003}.
An alternative method that does not approximate the binomial distribution by a normal one, is the Clopper-Pearson method~\citep{Clopper1934}.
In particular, this method relies upon the exact binomial distribution, which is why the method is often quoted as the `exact' method.
In particular, the $(1-\alpha)$  confidence bounds on $\eta$ are given by~\citep{Clopper1934}
\begin{align}
 \mathrm{CI}_{\mathrm{ClopperPearson}}  & \isdef \left[ \underline{\eta}, \overline{\eta} \right]\\
 \underline{\eta} &\isdef 
  \mathrm{CDF}_B^{-1}(\phantom{1-\;}\alpha/2; n_{\mathrm{success}}, N_{\MC} - n_{\mathrm{success}} + 1)\\
  \overline{\eta} &\isdef
  \mathrm{CDF}_B^{-1}(1-\alpha/2; n_{\mathrm{success}} + 1, N_{\MC} - n_{\mathrm{success}})
\end{align}
where $\mathrm{CDF}_B^{-1}(\alpha; n,m)$ denotes the inverse \gls{CDF} of a $\mathrm{Beta}(n,m)$ distribution.
This is known to yield somewhat conservative bounds, especially if only failures or successes are observed~\citep{Ross2003}.

@@

By aggregating the results for the different simulations and retaining the success rate $\eta$ only, a clearer view of the performance of the different methods is obtained.

>>>>

Parametric identification of \gls{LTI} systems from either input/output data or non-parametric frequency response data, has been well developed as evidenced by published literature~\citep{Pintelon2012,Ljung1999,Schoukens1999,Pintelon1998}.
Many of such parametric identification algorithms, however, require solving non-linear or non-convex optimization problems.
This often involves an iterative algorithm to produce the optimal model.
 The resulting model, however, depends on which initial estimates are used to start up the optimization process: typically one can end up in local minima, leading to models of sub-optimal quality.
 Hence, good initial estimates are essential to obtain a high quality model estimate.
 In this chapter, the \gls{MLE} is used as a proxy for any parametric transfer function estimator, since the \gls{MLE} is commonly used and has desirable properties such as efficiency and consistency.
 Since the initial value generation method are not specifically tailored towards the \gls{MLE}, other parametric identification frameworks are likely to benefit from these improved starting values as well.
 Hence, the presented approach is orthogonal to initialization schemes such as the work of \citet{vanHerpen2014}.

@@

The main aim and contribution of this chapter is to demonstrate that smoothing a measured \gls{FRF} non-parametrically, helps to avoid local optima during the parametric estimation of the \gls{MLE} of a transfer function, using classical (deterministic) optimization algorithms.
Hence, such techniques make it possible to increase the ``success rate'' (i.e. the probability that a good model, or even the global optimum, is obtained) of such a system identification step considerably.

@@

\paragraph{Outline}
The rest of the chapter is structured as follows. 
\secref{se:ProbForm} covers the problem formulation. 
\secref{se:MethodEg} presents the methodology for obtaining the initial estimates, and their influence on the success rate of the \gls{MLE}. 
This is followed by \secref{se:Demo} and \secref{se:ExpMeas}, which are demonstrations of the improved initial estimates on simulation and experimental data, respectively.
In \secref{se:Generality} the generality of the results is investigated briefly.
The computational effort and recommendations for practical implementations are given in \secref{sec:initvals:computation}.
Ultimately, concluding remarks are presented in \secref{se:Conclusion}.

\section{Problem formulation}\label{se:ProbForm}

@@

The maximum likelihood estimate of the parameter vector $\theta$  containing the coefficients of the $A$, $B$ and $I$  polynomials is obtained by solving the optimization problem
\begin{equation}
  \hat{\theta} = \arg\min_\theta V(\theta) \text{.}
\end{equation}
Since the noise $v(t)$ is assumed to be Gaussian, $V(\theta)$ accords to the weighted least squares cost function~\citep[Section 9.11]{Pintelon2012}:
\begin{equation}\label{eq:MLEcf}
V(\theta) = \sum_{k=1}^{N/2-1}\frac{|\varepsilon(k,\theta)|^2}{\sigma_\varepsilon^2(k,\theta)}
\end{equation}
for $N$ measurements and when $\varepsilon$ denotes the error in equation \eqref{DFTspectra},  \emph{viz}.:
\begin{align}
\varepsilon(k,\theta) = A(k,\theta)Y(k) - B(k,\theta)U(k) - I(k,\theta)\text{.}
\end{align}
The variance of the error is of the form:
\begin{equation}\label{eq:sigmaEps}
\begin{split}
\sigma_\varepsilon^2(k,\theta) 
  &=  |A(k,\theta)|^2\sigma_Y^2(k) 
   +  |B(k,\theta)|^2\sigma_U^2(k) \\
  &- 2\RealPart \left( A(k,\theta) \overline{B(k,\theta)} \sigma_{YU}(k) \right)
\end{split}
\end{equation}
where $\sigma_Y^2$ is independent of $k$ for white noise, and the input error variance is assumed to be zero, i.e. $\sigma^2_U=0$, and similarly, the covariance $\sigma_{YU} = 0$.
Here, $\overline{B}$ denotes the complex conjugate of $B$.

@@

@@

%\JL{
The \gls{RFIR} estimator is formulated in the time domain. 
It estimates the impulse response of a discrete time system as the minimizer of the following regularized least squares objective function:
\begin{align}\label{eq:hRFIRdef}
\hat g_{\mathrm{RFIR}} &= \argmin_{g} \norm{y - g \ast u }^2 + \sigma^2 g^{\TT}P^{-1}g
\end{align}
where $g$ is the vectorized impulse response $g(t)$, with $t = 0,1,\cdots,n_h - 1$, assuming that the impulse response is $n_g$ samples long. 
Furthermore, $g\ast u$ is the convolution of $g$ with the input signal $u$, and $P\in \mathbb{R}^{n_g\times n_g}$ is the kernel matrix~\citep{Chen2012}. 
Note that \eqref{eq:hRFIRdef} is quadratic in $g$, such that $\hat g_{\mathrm{RFIR}}$ can be computed analytically in a single step.
The kernel matrix $P$ embodies prior knowledge on the system to be estimated. 
Here, the \gls{DCkernel}~\citep{Chen2012,Pillonetto2010} is used. 
Specifically, the element at $t_1,t_2$ of $P$ is given by
\begin{equation}
P(\alpha,\beta)_{t_1,t_2} = e^{-\alpha|t_1 - t_2|}e^{-\beta(t_1 + t_2)/2}
\end{equation}
 for $t_1,t_2 \in \left\{0,1,\cdots,n_h - 1\right\}$ which makes the estimated impulse response to be an exponentially decaying function of $t$ with decay rate $\beta^{-1}$, and correlation length $\alpha^{-1}$. 
 The latter \emph{hyperparameters} $\alpha$, $\beta$ and $\sigma$ are determined using Empirical Bayes~\citep{Carlin2000,Gelman2014}, i.e. as the maximizers of the \gls{LML} of the measured output signal~\citep{Chen2012}:
\begin{align}
\mathrm{LML}(y) = -y^{\TT}\Sigma(\alpha,\beta,\sigma)^{-1}y - \log |\Sigma(\alpha,\beta,\sigma)| \text{,}
\end{align}
where $\Sigma(\alpha,\beta, \sigma) = \sigma^2 \I + \phi^{\TT}P(\alpha,\beta)\phi$ and $\phi$ is a Toeplitz matrix constructed with $u$. 
This problem is solved using \mcode{fmincon} in \MATLAB.

An implementation of the \gls{RFIR} estimator is available as the \mcode{arx} function in the System Identification Toolbox since \MATLAB~2013b with $\mathtt{na} = 0$, $\mathtt{nb} = n_g$, $\mathtt{nk}=0$ and regularization enabled in \mcode{arxOptions}. 
The hyperparameters can be determined via \mcode{arxRegul}.
More information about the \gls{RFIR} estimator can be found in
~\citep{Pillonetto2010,Chen2012}. 
The \gls{DFT} of the obtained regularized estimate of the impulse response $\hat g_{\mathrm{RFIR}}$ of the system yields a smoothed estimate of the \gls{FRF}.
\end{enumerate}

@@

A particular initial estimate is deemed \emph{successful} if the optimization of the MLE cost with the raw input-output data inserted in equation~\eqref{eq:MLEcf}, approximately reaches the \emph{best local optimum} when iteration is initiated with the selected initial value/estimate.

@@

The capability is quantified by defining the success rate of the initial estimate as the probability that the identification algorithm reaches the \emph{best local optimum} when the selected initial estimate is used. 
Note that probability in this context should be understood with respect to different realizations of the input signal and disturbing noise.

The success rate $\successRate_{\bullet}$ of an initialization scheme $\bullet$ is expressed mathematically as the probability function
\begin{equation}
\successRate_{\bullet} = 
  \Prob{  \model{\bullet}=\model{\trueSymbol}  }
\text{.}
\end{equation}
In practice, and since the iterative algorithm usually does not reach the local optimum precisely, the above definition is relaxed to the form
\begin{equation}\label{eq:successrateTol}
\successRate_{\bullet} \isdef \Prob{ \norm[2]{\model{\bullet} - \model{\trueSymbol}} < \absoluteTolerance}
\end{equation}
with $\absoluteTolerance$ a numerical tolerance that will be specified later on.

\begin{remark}
For an automated approach, it is better to define the success rate in terms of relative errors on the transfer function, i.e.
\begin{equation}
\successRate_{\bullet} = \Prob{ \norm[2]{\model{\bullet}-\model{\trueSymbol}} < \relativeTolerance  \norm[2]{\true{G}}}
\text{.}
\end{equation}
\end{remark}
\begin{remark}
In this chapter, the absolute criterion is used.
However, the results are equivalent for a relative criterion when the separation between successful and failed estimates is large since then observed success rate $\successRate$ is not sensitive towards the tolerance $\absoluteTolerance$ (or $\relativeTolerance$) when the tolerance is chosen with care.
Consequently, one can easily determine the equivalent relative tolerance from the absolute one using $\absoluteTolerance = \relativeTolerance \norm[2]{\true{G}}$.
\end{remark}

\begin{remark}

\end{remark}

% \comment{JL to EG: It is better to implement the success rate as given in \eqref{eq:successrateTol}, because that can more easily be adhered. Note that it is not obvious to determine a gerance on the difference between the estimated and the true model, because that depends on the noise variance of the estimate. On the other hand, the tolerance in \eqref{eq:successrateTol} and \eqref{eq:toldef} is independent of the noise variance.
%\comment{\EG{it is implemented that way now}}
% }

The $\mathcal{L}_2$ norm used in equation \eqref{eq:successrateTol} is defined~\citep{Skogestad2005} as
\begin{align}
\norm[2]{G(z)} &\isdef \sqrt{\frac{1}{2\pi}\int_0^{2\pi} |G(e^{-j\omega})|^2\ \mathrm{d}\omega}& \text{ for discrete time,}\\
\norm[2]{G(s)} &\isdef \sqrt{\frac{1}{2\pi}\int_{-\infty}^{+\infty} |G(j\omega)|^2\ \mathrm{d}\omega}& \text{ for continuous time}
\end{align}
 which, in practice, is computed by using the adaptive global quadrature algorithm provided by the MATLAB function \code{integral}.
The success rate in equation \eqref{eq:successrateTol} is estimated via Monte Carlo simulations in  Section \ref{se:CompuSR}.
\section{Demonstration}\label{se:Demo}

@@

\subsubsection{Simulation}
A Monte Carlo simulation was set up to determine the success rate of the estimator with different initial estimates for the following ranges %\comment{ML: To modify text!}
\begin{itemize}
\item of SNR: 
              $-20   \unit{dB}$, 
              $-16.7 \unit{dB}$, 
              $-13.3 \unit{dB}$, 
              $-10   \unit{dB}$, 
              $- 7.8 \unit{dB}$, 
              $- 5.6 \unit{dB}$, 
              $- 3.3 \unit{dB}$, 
              $- 1.1 \unit{dB}$, 
              $  1.1 \unit{dB}$, 
              $  3.3 \unit{dB}$, 
              $  5.6 \unit{dB}$, 
              $  7.8 \unit{dB}$, 
              $ 10   \unit{dB}$, 
              $ 13.3 \unit{dB}$, 
              $ 16.7 \unit{dB}$ and
              $ 20   \unit{dB}$
\item of number of samples $N$ is $3\,368$ or $4\,462$ for the first system whose quality factor $Q= 6 \unit{dB}$,
\item and of number of samples $N$ is $20\,250$ or $26\,792$ for the second system whose quality factor $Q = 20\unit{dB}$.
\end{itemize}
\TODO{johan: tijdsconstantes geven}
One can, equivalently, express the experiment length as the number $N_{3\unit{dB}}$ of frequency bins that lie within the $3\unit{dB}$ bandwidth of the system.
The $3\unit{dB}$ bandwidth is defined as the frequency band where the magnitude of the transfer function is, at most, $3\unit{dB}$ below its maximum as indicated in \figref{fig:exampleFRF}.
For both systems, $N$ was chosen such that $N_{3\unit{dB}}$ is respectively $36$ or $48$.
For each value-pair $(\SNR, N_{3\mathrm{dB}})$ and both systems, $n_{\mathrm{MC}} = 200$  simulations and estimations were performed.
Each individual simulation yields an estimate of the model based on which one can determine whether the estimation was successful or not.
This allows to empirically estimate the success rate $\successRate$ in equation \eqref{eq:successrateTol} as the proportion of the successes from the $N_{\MC} = 200$ runs.

%\ML{
\subsubsection{Illustrative Example}
In particular, the simulation for each pair $(\mathrm{SNR}, N_{3\mathrm{dB}})$ yields 200 estimates per initial value strategy.
This is illustrated graphically in \figref{fig:single-sim} for the value-pair $(-1.1\unit{dB},48)$ of the system with $Q = 6 \unit{dB}$, where the obtained distances $\norm[2]{\model{\bullet} - \model{\trueSymbol}}$ are shown for the different strategies, and sorted by an ascending norm.
This effectively shows an empirical cumulative distribution function of the distance measure $\norm[2]{\model{\bullet} - \model{\trueSymbol}}$ as sampled by the Monte Carlo algorithm.%}

%\JL{One observes:}
\subsubsection{Pertinent Observations}
With reference to \figref{fig:single-sim}, the following observations are worth noting: 
%\EG{
\begin{itemize}
\item The actual parametric estimates, based on the different initial estimates, have distinct behaviors with respect to their distance from $\model{\trueSymbol}$.
Two major classifications can be made:
\begin{enumerate}
  \item `good' estimates which have $\norm[2]{\model{\bullet} - \model{\trueSymbol}} < \absoluteTolerance \approx 6 \cdot 10^{-5}$,
  \item `poor' estimates which are much further from $\model{\trueSymbol}$.  This is caused by the local optima.
\end{enumerate}
\item
The obvious jump of the observed distances of the final parametric estimates shows that both classes can be separated reliably.
The index at which this jump occurs is a direct (visual) indication of the success rate $\successRate$ of the corresponding strategy to obtain initial values.
This indicates $\frac{147}{200} \approx 74\%$ success for the existing methods, $\frac{189}{200} \approx 95\%$ for the truncation method and $100\%$ for RFIR in \figref{fig:single-sim}.
\end{itemize}
%}

@@

In \figref{fig:successRateVS_SNR36N3dB}, the success rate (and its $95\%$ confidence interval $\mathrm{CI}$) obtained from the Monte Carlo simulations is shown to compare the proposed method with previously existing approaches.
Note that the empirical count of successes $n_{\mathrm{success}}$ out of the $N_{\MC}$ total observations is binomially distributed with success rate $\successRate$.
The computation of confidence bounds of such a variable is not obvious due to the discrete nature of the variable: $n_{\mathrm{success}}$ can only attain a discrete set of values: $\Set{0,1,\ldots, N_{\MC}}$ whereas the true success rate $\successRate$ is real-valued (but limited to the interval $[0,1]$).
The inherent discreteness of $\hat{\successRate} \isdef n_{\mathrm{success}}/N_{\MC}$ and the difficulties this presents has sparked a fair amount of research to compute confidence bounds~\citep{Barnard1947Significance,Mato1997,Ross2003,Clopper1934}.
A simple way to deal with this problem, is to make use of the central limit theorem which states that $n_{\mathrm{success}}/N_{\MC}$ is approximately normally distributed when $N_{\MC} \to \infty$.
In doing so, one e.g. obtains the Wald confidence bounds~\citep{Ross2003}:
\begin{equation}
\mathrm{CI}_{\mathrm{Wald}} \isdef \hat{\successRate} \pm z_{1-\alpha/2} \sqrt{\hat{\successRate} (1-\hat{\successRate}/N_{\MC})}
\end{equation}
with $\alpha = 1 - 0.95$ for $95\%$ confidence bounds and $z_{1-\alpha/2}$ is the $1-\alpha/2$ quantile of a standard normal distribution, i.e. $z_{\beta} \isdef \mathrm{CDF}_{\NormalDistribution}^{-1}(\beta)$
which requires inversion of the \gls{CDF} of a normal distribution.
However, such an approximation is overly optimistic when $n_{\mathrm{success}}$ approaches the boundaries of its domain (i.e. when $\successRate \approx 0$ or $\successRate \approx 1$) since normal confidence regions are always symmetrical whereas the actual success rate is inherently bounded as $0 \leq \successRate \leq 1$~\citep{Ross2003}.
An alternative method that does not approximate the binomial distribution by a normal one, is the Clopper-Pearson method~\citep{Clopper1934}.
In particular, this method relies upon the exact binomial distribution, which is why the method is often quoted as the `exact' method.
In particular, the $(1-\alpha)$  confidence bounds on $\successRate$ are given by~\citep{Clopper1934}
\begin{align}\label{eq:initvals:Binomial:CI}
 \mathrm{CI}_{\mathrm{ClopperPearson}}  & \isdef \left[ \underline{\successRate}, \overline{\successRate} \right]\\
 \underline{\successRate} &\isdef 
  \mathrm{CDF}_B^{-1}(\phantom{1-\;}\alpha/2; n_{\mathrm{success}}, N_{\MC} - n_{\mathrm{success}} + 1)\\
  \overline{\successRate} &\isdef
  \mathrm{CDF}_B^{-1}(1-\alpha/2; n_{\mathrm{success}} + 1, N_{\MC} - n_{\mathrm{success}})
\end{align}
where $\mathrm{CDF}_B^{-1}(\alpha; n,m)$ denotes the inverse \gls{CDF} of a $\mathrm{Beta}(n,m)$ distribution. %TODO: maybe add reference for Beta distribution
This is known to yield somewhat conservative bounds, especially if only failures or successes are observed~\citep{Ross2003}.

@@

By aggregating the results for the different simulations and retaining the success rate $\successRate$ only, a clearer view of the performance of the different methods is obtained.
